\documentclass[a4paper, 12pt]{paper}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{titlesec}
\usepackage{fullpage}
\usepackage{tikz-cd}
\usepackage{rotating}
\usepackage{pdflscape}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{diagbox}
\usepackage[left=.5in,right=.5in,top=.5in,bottom=.5in]{geometry}
\usepackage{enumitem}
\usepackage[colorlinks]{hyperref}
\usepackage{bussproofs}

\setitemize{topsep=3pt,parsep=5pt,partopsep=0pt,label=,leftmargin=1.3pc}
\titleformat{\section}[runin]{\normalfont\bfseries}{\thesection}{0.5em}{}
\titlespacing{\section}{0pc}{1.5ex plus .1ex minus .2ex}{1pc}
\titleformat{\subsection}[runin]{\normalfont\bfseries}{\thesubsection}{0.7em}{}
\titlespacing{\subsection}{0pc}{2ex plus .1ex minus .2ex}{1pc}
\titleformat{\subsubsection}[runin]{\normalfont\bfseries}{\thesubsubsection}{0.7em}{}
\titlespacing{\subsubsection}{0pc}{2ex plus .1ex minus .2ex}{1pc}
\newcommand\eqn{\refstepcounter{equation}\tag{\theequation}}
\binoppenalty=\maxdimen
\relpenalty=\maxdimen
\newcommand{\ul}{\ulcorner}
\newcommand{\ur}{\urcorner}
\newcommand{\val}[1]{\ulcorner len1 \urcorner}
\newcommand{\caseref}[1]{\hyperref[#1]{\ref{#1}}}
\newcommand{\rot}{\rotatebox{90}}
\EnableBpAbbreviations

\begin{document}
{\noindent
	v 0.3.2 \\
{\large\textbf{The Cut Rule Is Admissible in GSTL}}
}
\\
\setcounter{section}{-1}

\input{GSTL}

\section{Lemma}\label{true-assum} If $~\small\text{GSTL}^- + \nabla Cut \vdash \mathcal{S} \cup [\top^n | \epsilon_r] \Rightarrow \Delta$ then $\small\text{GSTL}^- + \nabla Cut \vdash \mathcal{S} \Rightarrow \Delta$ with a proof of at most the same rank.

\textit{Proof:} Suppose $\mathbf{D}$ is a proof tree for $\mathcal{S} \cup [\top^n | \epsilon_r] \Rightarrow \Delta$. By induction on $h(\mathbf{D})$, induction hypothesis states that for any proof tree $\mathbf{D}'$ with conclusion $\mathcal{S'} \cup [\top^{n'} | \epsilon_{r'}] \Rightarrow \Delta'$ such that $h(\mathbf{D}') < h(\mathbf{D})$, there is a proof $\mathbf{D}''$ of $\mathcal{S}' \Rightarrow \Delta'$ such that $\rho(\mathbf{D}'') \leq \rho(\mathbf{D}')$.

Consider different cases for the last rule of $\mathbf{D}$, with possible sub-trees $\mathbf{D_0}$ and $\mathbf{D_1}$. $Ta$ and $Ex$ cases are trivially ruled out. In $Id$ case (which implies $n = 1$ and $r = 0$), we have $\epsilon \Rightarrow \top$ by $Ta$. In $Lw$ case, where an instance of $\top$ is principal and $n = 1$, $\mathbf{D_0}$ itself proves the desired sequent. If $n > 1$, then the induction hypothesis with $n' = n - 1$ gives the desired sequent. $Lc$ on an instance of $\top$ is similar, with $n' = n + 1$. In all other cases, just apply induction hypothesis on $\mathbf{D_0}$ (and possibly $\mathbf{D_1}$), then the same last rule. Notice in all cases we must apply induction hypothesis with $n' = n$ and $r' = r$, except for $R\rightarrow$ and $R\nabla$, in which we apply it with $r' = r + 1$ and $r' = r - 1$ respectively. Also notice that $\nabla Cut$ is not used except in $\nabla Cut$ case, where it is applied with the same cut-formula, so the resulting proof tree is not of a higher rank than $\mathbf{D}$.

\section{Theorem}\label{cut-admis} \emph{Cut Reduction for GSTL: } For any $\mathcal{S}$, $n>0$, $A$, $\mathcal{T}$, $k$, $l$ and $\Delta$, if $~\small\text{GSTL}^- + \nabla Cut \vdash \mathcal{S} \Rightarrow \nabla^k A$ and $\small\text{GSTL}^- + \nabla Cut \vdash$ $\mathcal{T} \cup [A^n | \epsilon_{k+l}] \Rightarrow \Delta$ with proof trees of ranks less than $\rho(A)$, then
 $\small\text{GSTL}^- + \nabla Cut \vdash [ \mathcal{S} | \epsilon_l ] \cup \mathcal{T} \Rightarrow \Delta$ also with a proof tree of a rank less than $\rho(A)$.
 
\emph{Proof:}
Let $\mathbf{D_0}$ and $\mathbf{D_1}$ be proof trees of ranks less than $\rho(A)$, with conclusions $\mathcal{S} \Rightarrow \nabla^k A$ and $\mathcal{T} \cup [A^n | \epsilon_{k+l}] \Rightarrow \Delta$ and heights $h(\mathbf{D_0})$ and $h(\mathbf{D_1})$ respectively.
\begin{prooftree}
	\noLine
	\AXC{$\mathbf{D_0}$}
	\UIC{$\mathcal{S} \Rightarrow \nabla^k A$}
	
	\noLine
	\AXC{$\mathbf{D_1}$}
	\UIC{$\mathcal{T} \cup [A^n | \epsilon_{l+k}] \Rightarrow \Delta$}
	
	\dashedLine \RightLabel{$\nabla Cut$}
	\BIC{$[ \mathcal{S} | \epsilon_l ] \cup \mathcal{T} \Rightarrow \Delta$}
\end{prooftree}
By induction on $h(\mathbf{D_0}) + h(\mathbf{D_1})$, the induction hypothesis states that for any proof trees $\mathbf{D_0}'$ with conclusion $\mathcal{S}' \Rightarrow \nabla^{k'} A'$ and $\mathbf{D_1}'$ with conclusion $\mathcal{T}' \cup [A'^m | \epsilon_{k'+l'}] \Rightarrow \Delta'$ such that $h(\mathbf{D_0}') + h(\mathbf{D_1}') < h(\mathbf{D_0}) + h(\mathbf{D_1})$, if $\rho(\mathbf{D_0}'),\rho(\mathbf{D_1}') < \rho(A')$ then there exists a proof tree $\mathbf{D}'$ with conclusion $[ \mathcal{S}' | \epsilon_{l'} ] \cup \mathcal{T}' \Rightarrow \Delta'$ such that $\rho(\mathbf{D}') < \rho(A')$.

\input{table-cut-reduction-cases}

We proceed by case analysis on the last rule in $\mathbf{D_0}$. We can either apply the induction hypothesis on a pair of trees shorter than $\mathbf{D_0}$ and $\mathbf{D_1}$, or just cut a formula of a lower rank than $A$, to reach the desired sequent without increasing the cut-rank. This is easy when the cut-formula is also present in the immediate sub-tree(s) of $\mathbf{D_0}$, as it is the case for the left-rules. In these cases, we somehow ``commute'' the last rule of $\mathbf{D_0}$ with an application of induction hypothesis for its premise(s) and $\mathbf{D_1}$. In right-rule cases, where $A$ is principal and not present in the sub-tree(s) of $\mathbf{D_0}$, we consider further cases, this time for the last rule of $\mathbf{D_1}$. We can do the same with $\mathbf{D_1}$ in the cases that no instance of $A$ is principal in its last rule. Almost all other cases force a particular construction for $A$ so we can apply $\nabla Cut$ on its sub-formulas. The only exception is the case where $\mathbf{D_0}$ ends with $R \nabla$. The induction hypothesis is strong enough to handle this one in particular.

\begin{enumerate}
	\item ($Id$) \label{c:id-*} \input{case-left-id}

	\item ($Ta$) \label{c:ta-*} \input{case-left-ta}

	\item ($Lw$) \label{c:lw-*} \input{case-left-lw}

	\item ($Lc$) \label{c:lc-*} \input{case-left-lc}

	\item \label{c:cut-*} \input{case-left-cut}

	\item \label{c:la1-*} \input{case-left-la1}

	\item \label{c:la2-*} \input{case-left-la2}
	
	\item \label{c:lo-*} \input{case-left-lo}
	
	\item \label{c:ln-*} \input{case-left-ln}
	
	\item \label{c:li-*} \input{case-left-li}
	
	\item \label{c:rw-*} \input{case-left-rw}


	\item[13-17.] ($R*$) In the cases that the last rule in $\mathbf{D_0}$ is any of the logical right-rules $R*$ ($* \in \{ \land, \lor_{i}, \rightarrow, \nabla \}$), its principal formula would be $\nabla^k A$. The only admissible $R*$ with $k > 0$ would be $R\nabla$. For the other rules, this forces $k = 0$, plus a particular construction for $A$ based on the last rule. In each case, we will proceed by case analysis on the last rule of $\mathbf{D_1}$, but to avoid repeating similar cases, we will separate cases by whether the last rule of $\mathbf{D_1}$ is logical, and if $A$ is also the principal formula there or not. So we have the following groups of cases:
	(I) Cases in which $A$ is not principal in $\mathbf{D_1}$,
	(II) cases in which the last rule of $\mathbf{D_1}$ is any of the logical left-rules and (an instance of) $A$ is its principal formula, and (III) $A$ is principal in $\mathbf{D_1}$, but the rule is either structural or an axiom. Notice that the solution for the different cases of $\mathbf{D_1}$ in (I) and (III) is shared by all cases of $\mathbf{D_0}$, since it does not depend on the last rule of $\mathbf{D_0}$. This may seem like we have commuted the case analysis on $\mathbf{D_1}$ with the one on $\mathbf{D_0}$, which is not true. So each item in (I) or (III) handles many different cases with similar solutions.
	On the other hand, each case of $\mathbf{D_0}$ in (II) determines a single case for $\mathbf{D_1}$. The parens before each case show the last rule of $\mathbf{D_0}$ and $\mathbf{D_1}$ respectively.

	I. If $A$ is not principal in the last rule of $\mathbf{D_1}$.
	
	\begin{enumerate}[label={\alph*.}]
		\item \label{c:*-lw} \input{case-right-lw}
		
		\item \label{c:*-rw} \input{case-right-rw}
		
		\item \label{c:*-lc} \input{case-right-lc}

		\item \label{c:*-cut} \input{case-right-cut}


		\item \label{c:*-la1} \input{case-right-la1}
		
		\item \label{c:*-la2} \input{case-right-la2}
		
		\item \label{c:*-ra} \input{case-right-ra}
		
		\item \label{c:*-lo} \input{case-right-lo}
		
		\item \label{c:*-ro1} \input{case-right-ro1}
		
		\item \label{c:*-ro2} \input{case-right-ro2}
		
		\item \label{c:*-li} \input{case-right-li}
		
		\item \label{c:*-ri} \input{case-right-ri}
		
		\item \label{c:*-ln} \input{case-right-ln}
		
		\item \label{c:*-rn} \input{case-right-rn}
	
		II. If the last rule in $\mathbf{D_1}$ is a logical left-rule and $A$ is also principal there. In 

	\begin{enumerate}[label={\Alph*.}]
		\item \label{c:ra-la1} \input{case-ra-la1}

		\item \label{c:ra-la2} \input{case-ra-la2}

		\item \label{c:ro1-lo} \input{case-ro1-lo}

		\item \label{c:ro2-lo} \input{case-ro2-lo}

		\item \label{c:rn-*} \input{case-rn-ln}

		\item \label{c:ri-li} \input{case-ri-li}

	\end{enumerate}

	III. If $A$ is principal in the last rule of $\mathbf{D_1}$, which is not logical.
	\begin{enumerate}[label={\roman*.}]
		\item \label{c:*-id} \input{case-right-id-p}

		\item \label{c:*-ex} \input{case-right-ex-p}

		\item \label{c:*-lw-p} \input{case-right-lw-p}
	
		\item \label{c:*-lc-p} \input{case-right-lc-p}
	\end{enumerate}
\end{enumerate}

\section{Corollary} \emph{$\nabla$Cut Elimination for GSTL: }
If $\small\text{GSTL}^- + \nabla Cut \vdash \Gamma \Rightarrow \Delta$, then $\small\text{GSTL}^- \vdash \Gamma \Rightarrow \Delta$.

\emph{Proof:} It suffices to show that for any proof tree of $\Gamma \Rightarrow \Delta$ like $\mathbf{D}$, there is another proof of it with a lower rank. Using induction on $h(\mathbf{D})$, the induction hypothesis states that for any proof of $\Gamma' \Rightarrow \Delta'$ like $\mathbf{D'}$ such that $h(\mathbf{D'}) < h(\mathbf{D})$, there is another proof of $\Gamma' \Rightarrow \Delta'$ like $\mathbf{D''}$ such that $\rho(\mathbf{D''}) < \rho(\mathbf{D'})$. Particularly for the immediate sub-trees of $\mathbf{D}$, this gives us sub-trees with lower cut-rank, which we call $\mathbf{D}_i$. We now consider two cases for the last rule of $\mathbf{D}$

\begin{enumerate}[label=\Roman*]
	\item If the last rule of $\mathbf{D}$ is of a lower rank than $\rho(\mathbf{D})$, i.e. the $\nabla Cut$ rule with the maximum rank is not the last rule in $\mathbf{D}$, then we can apply the same last rule on $\mathbf{D}_i$s and get a proof of $\Gamma \Rightarrow \Delta$ with a lower rank.
	
	\item If the last rule of $\mathbf{D}$ is an instance of $\nabla Cut$ rule with a cut-formula of rank $\rho(\mathbf{D})$, then we can apply theorem \ref{cut-admis} to $\mathbf{D_0}$ and $\mathbf{D_1}$ to get the same $\nabla Cut$ with a lower rank.
\end{enumerate}

\end{document}
