\documentclass[12pt,a4paper]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
%\usepackage{fdsymbol}

\usepackage{authblk}

\usepackage[mathscr]{eucal}

\usepackage{bussproofs}
\EnableBpAbbreviations

\usepackage{amssymb}
\usepackage{tikz}
\usepackage{enumitem}
\tikzset{node distance=2cm, auto}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]

\renewcommand{\thethm}{\arabic{section}.\arabic{thm}}
\newtheorem{lem}[thm]{Lemma}

\newtheorem{cor}[thm]{Corollary}
\theoremstyle{definition}
\newtheorem{dfn}[thm]{Definition}
\newtheorem{exam}[thm]{Example}
\newtheorem{rem}[thm]{Remark}
\newtheorem{nota}[thm]{Notation}
\newtheorem{exer}[thm]{Exercise}

\def\d{\displaystyle}
\def\PA{\mathrm{PA}}
\def\Pr{\mathrm{Pr}}
\def\Prf{\mathrm{Prf}}
\def\PR{\mathrm{PR}}
\def\IPC{\mathrm{IPC}}
\def\Proofs{\mathrm{Proofs}}
\def\int{\mathrm{int}}
\def\WT{\mathrm{WT}}
\def\exp{\mathrm{exp}}
\def\CHaus{\mathrm{CHaus}}
\def\Fin{\mathrm{Fin}}
\def\E{\mathrm{E}}
\def\PR{\mathrm{PR}}
\def\Top{\mathrm{Top}}
\def\S4{\mathrm{S4}}
\def\Hom{\mathrm{Hom}}
\def\Set{\mathrm{Set}}

\begin{document}

\title{The Logic of Dynamic Locales}


\author[]{Amirhossein Akbar Tabatabai, Alireza Mahmoudian}

\affil[]{ }


\date{ }

\maketitle


\begin{abstract}
In this paper we will first introduce dynamic locales as the point-free intuitionistic version of the dynamic topological systems. Then we will introduce the logic of the dynamic locales, $\mathbf{LDL}$, as a base for the intuitionistic version for classical dynamic topological logic, introduced in \cite{Artemov}. We will then present cut-free sequent-style proof systems for the logic $\mathbf{LDL}$ and one of its important fragments. Using the systems, we will finally provide a syntactical proof for the admissibly of a natural extension of Visser rules and the appropriate interpolation property that these logic enjoy.
\end{abstract}

\section{Introduction}


\section{Dynamic Locales and Their Logic} \label{DynamicLocales}

\begin{dfn}
A locale $\mathscr{X}$ is a complete poset whose meet distributes over any arbitrary family of joins, i.e., $a \wedge \bigvee_{i \in I} b_i=\bigvee_{i \in I} (a \vee b_i)$, for any $a, b_i \in \mathscr{X}$. A localic map $f: \mathscr{X} \to \mathscr{Y}$ between two locales $\mathscr{X}$ and $\mathscr{Y}$ is a map preserving all finite meets and arbitrary joins. It is called an isomorphism if it has a converse as a localic map.
\end{dfn}

The canonical example of locales and the localic maps are the poset of the open subsets of a topological space and the inverse image of the continuous functions between spaces, respectively. In this sense, locales and the localic maps provide a point-free formalization for the topological discourse, focusing only on open subsets as the main ingredient of topology.

\begin{dfn}
Let $\mathscr{X}$ be a locale and $\nabla: \mathscr{X} \to \mathscr{X}$ be a localic map. Then $\mathcal{D}=(\mathscr{X}, \nabla)$ is called a dynamic locale. It is called invertible if $\nabla$ is an isomorphism.
\end{dfn}

Dynamic locales are the intuitionistic and simplified version of the dynamic topological spaces defined in \cite{}. Here, we force the formalization to restrict itself to the open subsets. However, to represent the non-elementary structure of dynamic locales in a syntactical elementary language, we need to capture the distributivity of meets over arbitrary joins and the fact that $\nabla$ preserves any arbitrary joins. The following easy observation helps:

\begin{thm}(Adjoint Functor Theorem for Posets) \label{AFT}
Let $\mathcal{A}$ and $\mathcal{B}$ be two complete posets and $f:\mathcal{A} \to \mathcal{B}$ be an order-preserving function. Then $f$ preserves arbitrary joins iff there exists an order-preserving function $g: \mathcal{B} \to \mathcal{A}$ such that
\[
f(a) \leq_{\mathcal{B}} b  \;\;\; \text{iff}  \;\;\; a \leq_{\mathcal{A}} g(b)
\]
This $g$ if exits is clearly unique and called the right adjoint of $f$.
\end{thm}
\begin{proof}
If there exists such $g$ then $f$ preserves all joins... For the other half, define $g(b)=\bigvee \{a \in \mathcal{A} | f(a) \leq_{\mathcal{B}} b \}$. One direction is obvious from the definition. The other is a consequence of the fact that $f$ preserves all joins.
\end{proof}

Using Theorem \ref{AFT} on a dynamic locale $\mathcal{D}=(\mathscr{X}, \nabla_{\mathcal{D}})$, we can observe that the facts that the maps $x \mapsto x \wedge a$ and $x \mapsto \nabla x$ preserve arbitrary joins, are representable by introducing their right adjoints into the language as the primitive connectives. For the former, the adjoint is nothing but the usual Heyting implication. For the latter, we need to add a new unary connective $\Box$ representing the function denoted by $\Box_{\mathcal{D}}$, satisfying
\[
\nabla_{\mathcal{D}} a \leq_{\mathscr{X}} b  \;\;\; \text{iff}  \;\;\; a \leq_{\mathscr{X}} \Box_{\mathcal{D}} b
\]

In the following, we will define the logic of dynamic locales, denoted by $\mathbf{LDL}$. Let $\mathcal{L}$ be the usual language of propositional logic plus the modalities $\nabla$ and $\Box$, i.e., $\mathcal{L}=\{\wedge, \vee, \to, \top, \bot, \nabla, \Box\}$. Define $\mathbf{LDL}$ as the logic of the sequent-style system defined by the following rules:
\begin{flushleft}
 \textbf{Axioms:}
\end{flushleft}
\begin{center}
 \begin{tabular}{c c c}
 \AxiomC{}
 \RightLabel{$Id$}
 \UnaryInfC{$ A \Rightarrow A$}
 \DisplayProof \;\;\;
 &
 \AxiomC{}
 \RightLabel{$Ta$}
 \UnaryInfC{$ \Rightarrow \top$}
 \DisplayProof\;\;\;
 &
 \AxiomC{}
 \RightLabel{$Ex$}
 \UnaryInfC{$ \bot \Rightarrow $}
 \DisplayProof
 \\[3ex]
\end{tabular}
\end{center}

\begin{flushleft}
 		\textbf{Structural Rules:}
\end{flushleft}

\begin{center}
 \begin{tabular}{c c c}
 \AxiomC{$ \Gamma \Rightarrow \Delta$}
 \RightLabel{$L w$}
 \UnaryInfC{$ \Gamma, A \Rightarrow \Delta$}
 \DisplayProof
 &
 \AxiomC{$ \Gamma \Rightarrow $}
\RightLabel{$R w$}
 \UnaryInfC{$\Gamma \Rightarrow A$}
 \DisplayProof
 &
 \AxiomC{$ \Gamma, A, A \Rightarrow \Delta$}
\RightLabel{$Lc$}
 \UnaryInfC{$\Gamma, A \Rightarrow \Delta$}
 \DisplayProof
  \\[3ex]
\end{tabular}
\end{center}

\begin{flushleft}
 		\textbf{Cut:}
\end{flushleft}
\begin{center}
  	\begin{tabular}{c}

		\AxiomC{$ \Gamma \Rightarrow A$}
		\AxiomC{$\Pi, A \Rightarrow \Delta$}
		\RightLabel{$cut$}
		\BinaryInfC{$ \Pi, \Gamma \Rightarrow \Delta$}
		\DisplayProof
		 \\[3ex]
		\end{tabular}
\end{center}

\begin{flushleft}
 \textbf{Conjunction Rules:}
\end{flushleft}
\begin{center}
 \begin{tabular}{c c c}
\AxiomC{$ \Gamma, A \Rightarrow \Delta$}
 \RightLabel{$L \wedge_1$}
 \UnaryInfC{$ \Gamma, A \wedge B \Rightarrow \Delta$}
 \DisplayProof
 &
 \AxiomC{$ \Gamma, B \Rightarrow \Delta$}
 \RightLabel{$L \wedge_2$}
 \UnaryInfC{$\Gamma, A \wedge B \Rightarrow \Delta$}
 \DisplayProof
	   		&
   		\AxiomC{$\Gamma \Rightarrow A$}
   		\AxiomC{$\Gamma \Rightarrow B$}
   		\RightLabel{$R \wedge$}
   		\BinaryInfC{$ \Gamma \Rightarrow A \wedge B $}
   		\DisplayProof
   			\\[3 ex]
\end{tabular}
\end{center}

\begin{flushleft}
 \textbf{Disjunction Rules:}
\end{flushleft}
\vspace{.001pt}
\begin{center}
 \begin{tabular}{c c c}
 \AxiomC{$ \Gamma, A \Rightarrow \Delta$}
 \AxiomC{$\Gamma, B \Rightarrow \Delta$}
 \RightLabel{$L \vee_1$}
 \BinaryInfC{$ \Gamma, A \vee B \Rightarrow \Delta$}
 \DisplayProof
 &
 \AxiomC{$\Gamma \Rightarrow A$}
 \RightLabel{$R \vee_2$}
 \UnaryInfC{$\Gamma \Rightarrow A \vee B$}
 \DisplayProof
 &
 \AxiomC{$\Gamma \Rightarrow B$}
 \RightLabel{$R \vee$}
 \UnaryInfC{$\Gamma \Rightarrow A \vee B$}
 \DisplayProof
 \\[3ex]
\end{tabular}
\end{center}

\begin{flushleft}
	\textbf{Implication Rules:}
 \end{flushleft}
 \vspace{.001pt}
 \begin{center}
	\begin{tabular}{c c c}
	\AxiomC{$ \Gamma \Rightarrow A$}
	\AxiomC{$\Gamma, B \Rightarrow \Delta$}
	\RightLabel{$L \rightarrow$}
	\BinaryInfC{$ \Gamma, A \rightarrow B \Rightarrow \Delta$}
	\DisplayProof
	&
	\AxiomC{$\Gamma , A \Rightarrow B$}
	\RightLabel{$R \rightarrow$}
	\UnaryInfC{$\Gamma \Rightarrow A \rightarrow B$}
	\DisplayProof
	\\[3ex]
 \end{tabular}
 \end{center}

\begin{flushleft}
  \textbf{$\nabla$ Rules:}
\end{flushleft}
\vspace{.001pt}
\begin{center}
 \begin{tabular}{c}
 \AxiomC{$\Gamma \Rightarrow A$}
 \RightLabel{$N$}
 \UnaryInfC{$\nabla \Gamma \Rightarrow \nabla A$}
 \DisplayProof
 \\[3ex]
\end{tabular}
\end{center}

\begin{flushleft}
 \textbf{$\Box$ Rules:}
\end{flushleft}
\vspace{.001pt}
\begin{center}
 \begin{tabular}{c c}
 \AxiomC{$\Gamma, A \Rightarrow \Delta$}
 \RightLabel{$L \Box$}
 \UnaryInfC{$\Gamma, \nabla \Box A \Rightarrow \Delta$}
 \DisplayProof
 &
 \AxiomC{$\nabla \Gamma \Rightarrow A$}
 \RightLabel{$R \Box$}
 \UnaryInfC{$\Gamma \Rightarrow \Box A$}
 \DisplayProof
 \\[3ex]
\end{tabular}
\end{center}
If we also add the following rules to the system we have some variants of $\mathbf{LDL}$; \textbf{LDL(L)}, \textbf{LDL(R)}, \textbf{LDL(F)} and \textbf{LDL(Fu)} respectively.


\textbf{L}
\begin{prooftree}
	\RightLabel{$L$}
	\AXC{$\Gamma, A \Rightarrow \Delta$}
	\UIC{$\Gamma, \nabla A \Rightarrow \Delta$}
\end{prooftree}

\textbf{R}
\begin{prooftree}
	\RightLabel{$R'$}
	\AXC{$\nabla \Gamma, \Sigma \Rightarrow \Delta$}
	\UIC{$\Gamma, \Sigma \Rightarrow \Delta$}
\end{prooftree}

\textbf{Fa}
\begin{prooftree}
	\RightLabel{$Fa$}
	\AXC{$\Gamma \Rightarrow A$}
	\UIC{$\Gamma \Rightarrow \nabla \Box A$}
\end{prooftree}

\textbf{Fu}
\begin{prooftree}
	\RightLabel{$Fu'$}
	\AXC{$\nabla \Gamma \Rightarrow \nabla A$}
	\UIC{$\Gamma \Rightarrow A$}
\end{prooftree}

\begin{dfn}\label{t4-1}(Topological Semantics)
Let $\mathcal{D}=(\mathscr{X}, \nabla_{\mathcal{D}})$ be a dynamic locale and $V:\mathcal{L} \to\mathscr{X}$ be an assignment. A tuple $(\mathcal{D}, V)$ is called a topological model if:
\begin{itemize}
\item[$\bullet$]
$V(\top)=1$ and $V(\bot)=0$,
\item[$\bullet$]
$V(A \wedge B)=V(A) \wedge V(B)$,
\item[$\bullet$]
$V(A \vee B)=V(A) \vee V(B)$,
\item[$\bullet$]
$V(\nabla A)=\nabla_{\mathcal{D}} V(A)$,
\item[$\bullet$]
$V(\Box A)= \Box_{\mathcal{D}} V(A)$.
\end{itemize}
We say $(\mathcal{D}, V) \vDash \Gamma \Rightarrow \Delta$ when $\bigwedge_{\gamma \in \Gamma} V(\gamma) \leq \bigvee_{\delta \in \Delta} V(\delta)$ and $\mathcal{D} \vDash \Gamma \Rightarrow \Delta$ when for all $V$, $(\mathcal{D}, V) \vDash \Gamma \Rightarrow \Delta$.
\end{dfn}

\begin{thm}\label{t4-2}(Soundness-Completeness)
\begin{itemize}
\item[$(i)$]
$ \mathbf{LDL} \vdash \Gamma \Rightarrow \Delta$ iff $\mathcal{D} \vDash \Gamma \Rightarrow \Delta$, for any dynamic locale $\mathcal{D}$.
\item[$(ii)$]
$ \mathbf{LDL}(H) \vdash \Gamma \Rightarrow \Delta$ iff $\mathcal{D} \vDash \Gamma \Rightarrow \Delta$,  for any invertible dynamic locale $\mathcal{D}$.
\end{itemize}

\end{thm}
\begin{proof}
Basically refer to \cite{Amir}.
\end{proof}

\subsection{Kripke Models} \label{KripkeModels}

\begin{dfn}
By a Kripke model for the language $\mathcal{L}$, we mean a tuple $\mathcal{K}=(W, \leq, R, V)$ where $(W, \leq)$ is a poset, $R \subseteq W \times W$ is a relation over $W$ (not necessarily transitive or reflexive) compatible with $\leq$, i.e., for all $u, u', v, v' \in W$ if $(u, v) \in R$ and $u' \leq u$ and $v \leq v'$ then $(u', v') \in R$ and $V: At(\mathcal{L}) \to U((W, \leq))$, where $At(\mathcal{L})$ is the set of atomic formulas of $\mathcal{L}$ and $U((W, \leq))$ is the set of all upsets of $(W, \leq)$. Define the forcing relation as usual using the relation $\leq$ for the intuitionistic implication and $R$ for $\Box$, and for the $\nabla$ let $u \Vdash \nabla A$ if there exists $v \in W$ such that $(v, u) \in R$ and $v \Vdash A$. A Kripke model is called normal if there exists an order preserving function $\pi : W \to W$ such that $(u, v) \in R$ iff $u \leq \pi(v)$. It is clear that if this $\pi$ exists, it would be unique. Finally, a sequent $\Gamma \Rightarrow \Delta$ is valid in a Kripke model if for all $w \in W$, $w \Vdash \bigwedge \Gamma$ implies $w \Vdash \bigvee \Delta$.
\end{dfn}

\begin{thm}(Soundness-Completeness)
\begin{itemize}
\item[$(i)$]
The logic $\mathbf{LDL}$ is sound and complete with respect to all normal Kripke models.
\item[$(ii)$]
The logic $\mathbf{LDL}(H)$ is sound and complete with respect to all normal Kripke models whose functions $\pi$ are order-isomorphism.
\end{itemize}
\end{thm}

\subsection{The Fragment $\mathbf{LDL}_{\rightsquigarrow}$}
In this subsection we will introduce a fragment of the logic $\mathbf{LDL}$. To explain why we find this fragment interesting, let us begin with a formalization for a general notion of implication, introduced in \cite{Amir}:
\begin{dfn}
Let $\mathcal{A}=(A, \leq, \wedge, 1)$ be a meet semi-lattice. A map $\rightsquigarrow : A^{op} \times A \to A$ is called a meet-internalizing implication if:
\begin{itemize}
\item[$\bullet$]
$a \rightsquigarrow a=1$, for any $a \in A$.
\item[$\bullet$]
$(a \rightsquigarrow b) \wedge (b \rightsquigarrow c) \leq (a \rightsquigarrow c)$, for any $a, b, c \in A$.
\item[$\bullet$]
$(a \rightsquigarrow b) \wedge (a \rightsquigarrow c)= a \rightsquigarrow (b \wedge c)$, for any $a, b, c \in A$.
\end{itemize}
The tuple $(A, \leq, \wedge, 1, \rightsquigarrow)$ is called a meet-internalizing strong algebra. An embedding from a meet-internalizing strong algebra $(A, \leq_A, \wedge_A, 1_A, \rightsquigarrow_A)$ to another meet-internalizing strong algebra $(B, \leq_B, \wedge_B, 1_B, \rightsquigarrow_B)$ is a map $i : A \to B$, preserving all structures such that if $i(a) \leq_B i(b)$ then $a \leq_A b$.
\end{dfn}
The main source to produce these implications is dynamic locales. Let $\mathcal{D}=(\mathscr{X}, \nabla)$ be a dynamic locale. Then define $a \rightsquigarrow_{\nabla} b=\Box_{\mathcal{D}}(a \to b)$. It is not hard to show that this binary operation is a meet-internalizing implication. Denote this meet-internalizing strong algebra by $\mathcal{A}(\mathcal{D})$. The following theorem, proved in \cite{Amir}, shows that this example is essentially the only example we may have:
\begin{thm}(Representation theorem)
Let $\mathcal{A}=(A, \wedge, \rightsquigarrow)$ be a meet-internalizing strong algebra. Then there exists a dynamic locale $\mathcal{D}=(\mathscr{X}, \nabla)$ and an embedding $i: \mathcal{A} \to \mathcal{A}(\mathcal{D})$.
\end{thm}

This representation theorem justifies focusing on the fragment of $\mathbf{LDL}$, where the implication $\rightsquigarrow$ is present and the usual intuitionistic implication and $\Box$ are both omitted. Note that the representation theorem implies that the study of such a fragment is actually the study of all possible meet-internalizing implications. It is also possible to omit the modality $\nabla$ to have a more faithful syntax for implications. This is an established approach in sub-intuitionistic logic community. However, the draw back here is that in the absence of $\nabla$, the implication becomes proof-theoretically ill-behaved.\\

Define the fragment $\mathbf{LDL}_{\rightsquigarrow}$ of $\mathbf{LDL}$ as the system over the language $\mathcal{L}_{\rightsquigarrow}=\mathcal{L}-\{\to, \Box\} \cup \{\rightsquigarrow\}$, consisting of the axioms, structural rules and propositional rules and the rule $N$ of $\mathbf{LDL}$,  together with the following rules for $\rightsquigarrow$:

\begin{flushleft}
 \textbf{Implication Rules:}
\end{flushleft}
\vspace{.001pt}
\begin{center}
 \begin{tabular}{c c}
 \AxiomC{$\Gamma \Rightarrow A$}
 \AxiomC{$\Gamma, B \Rightarrow \Delta$}
 \RightLabel{$L \rightsquigarrow$}
 \BinaryInfC{$\Gamma, \nabla (A \rightsquigarrow B) \Rightarrow \Delta$}
 \DisplayProof
 &
 \AxiomC{$\nabla \Gamma, A \Rightarrow B$}
 \RightLabel{$R \rightsquigarrow$}
 \UnaryInfC{$\Gamma \Rightarrow A \rightsquigarrow B$}
 \DisplayProof
 \\[3ex]
\end{tabular}
\end{center}

$\mathbf{LDL}_\rightsquigarrow$ also has the same variants as $\mathbf{LDL}$, except for $Fa$, which is

\textbf{Fa$_\rightsquigarrow$}
\begin{prooftree}
	\RightLabel{$Fa_\rightsquigarrow$}
	\AXC{$\Gamma , A \Rightarrow B$}
	\UIC{$\Gamma \Rightarrow \nabla(A \rightsquigarrow B)$}
\end{prooftree}


\begin{thm}
The systems $\mathbf{LDL}$ and $\mathbf{LDL}(H)$ are conservative extensions of the systems $\mathbf{LDL}_{\rightsquigarrow}$ and $\mathbf{LDL}_{\rightsquigarrow}(H_\rightsquigarrow)$, respectively.
\end{thm}
\begin{proof}
Write the easier part. The harder part must be essentially to completeness theorems of \cite{Amir}.
\end{proof}


\section{Proof Theory of $\mathbf{LDL}$ and $\mathbf{LDL}_{\rightsquigarrow}$}

\subsection{Sequent-style Systems}
In this section we will introduce two slightly modified systems $\mathbf{LDL}^*$ and $\mathbf{LDL}_{\rightsquigarrow}^*$, equivalent to $\mathbf{LDL}$ and $\mathbf{LDL}_{\rightsquigarrow}$ respectively. Their advantage is that they are, as it will be shown, cut-free.

Define $\mathbf{LDL}^*$ on the language $\mathcal{L}$, as the logic of the sequent-style system define by the same rules of $\mathbf{LDL}$, except the rules $Ex$, $L\wedge_1$, $L\wedge_2$, $L\vee$, $L\rightarrow$, $N$ and $L\Box$, which are replaced by the following generalized rules respectively:

	 \begin{center}
		\begin{tabular}{c}
		\AxiomC{}
		\RightLabel{$Ex$}
		\UnaryInfC{$\nabla^n \bot \Rightarrow$}
		\DisplayProof
		\\[3ex]
	 \end{tabular}
	 \end{center}

	 \begin{center}
		\begin{tabular}{c c}
	 \AxiomC{$\Gamma, \nabla^n A \Rightarrow \Delta$}
		\RightLabel{$L \wedge_1$}
		\UnaryInfC{$\Gamma, \nabla^n (A \wedge B) \Rightarrow \Delta$}
		\DisplayProof
		&
		\AxiomC{$ \Gamma, \nabla^n B \Rightarrow \Delta$}
		\RightLabel{$L \wedge_2$}
		\UnaryInfC{$\Gamma, \nabla^n (A \wedge B) \Rightarrow \Delta$}
		\DisplayProof
		\\[3 ex]
	 \end{tabular}
	 \end{center}

	 \vspace{.001pt}
	 \begin{center}
		\begin{tabular}{c}
		\AxiomC{$\Gamma, \nabla^n A \Rightarrow \Delta$}
		\AxiomC{$\Gamma, \nabla^n B \Rightarrow \Delta$}
		\RightLabel{$L \vee$}
		\BinaryInfC{$\Gamma, \nabla^n (A \vee B) \Rightarrow \Delta$}
		\DisplayProof
		\\[3ex]
	 \end{tabular}
	 \end{center}

	 \vspace{.001pt}
	 \begin{center}
		\begin{tabular}{c c}
		\AxiomC{$ \Gamma \Rightarrow \nabla^n A$}
		\AxiomC{$\Gamma, \nabla^n B \Rightarrow \Delta$}
		\RightLabel{$L \rightarrow$}
		\BinaryInfC{$ \Gamma, \nabla^n (A \rightarrow B) \Rightarrow \Delta$}
		\DisplayProof
		\\[3ex]
	 \end{tabular}
	 \end{center}

	 \vspace{.001pt}
	 \begin{center}
		\begin{tabular}{c}
		\AxiomC{$\Gamma \Rightarrow \Delta$}
		\RightLabel{$N$}
		\UnaryInfC{$\nabla \Gamma \Rightarrow \nabla \Delta$}
		\DisplayProof
		\\[3ex]
	 \end{tabular}
	 \end{center}

	 \vspace{.001pt}
	 \begin{center}
		\begin{tabular}{c}
		\AxiomC{$\Gamma, \nabla^n A \Rightarrow \Delta$}
		\RightLabel{$L \Box$}
		\UnaryInfC{$\Gamma, \nabla^{n+1} \Box A \Rightarrow \Delta$}
		\DisplayProof
		\\[3ex]
	 \end{tabular}
	 \end{center}

Similarly for $\mathbf{LDL}_{\rightsquigarrow}$, the equivalent but cut-free logic $\mathbf{LDL}^*_{\rightsquigarrow}$ is defined on the language $\mathcal{L}_{\rightsquigarrow}$, by replacing $Ex$, $L\wedge_1$, $L\wedge_2$, $L\vee$ and $N$ by exactly the same generalized rules as above, and also $L\rightsquigarrow$ by the following rule:

\begin{prooftree}
	\AXC{$\Gamma \Rightarrow \nabla^n A$}
	\AXC{$\Gamma, \nabla^n B \Rightarrow \Delta$}
	\RightLabel{$L \rightsquigarrow$}
	\BIC{$\Gamma, \nabla^{n+1} (A \rightsquigarrow B) \Rightarrow \Delta$}
\end{prooftree}

The following lemmas are used in the subsequent theorem, to show that $\mathbf{LDL}^*$ has exactly the same power as $\mathbf{LDL}$.

\begin{lem}\label{lem:l-nabla-dist-and} For all $n > 0$, $\mathbf{LDL} \vdash \nabla^n (A \land B) \Rightarrow \nabla^n A \land \nabla^n B$.
\end{lem}
\begin{proof}\quad
	\begin{prooftree}
		\AXC{}
		\RightLabel{$Id$}
		\UIC{$A \Rightarrow A$}
		\RightLabel{$L\land_1$}
		\UIC{$A \land B \Rightarrow A$}
		\RightLabel{$N$} \doubleLine
		\UIC{$\nabla^n (A \land B) \Rightarrow \nabla^n A$}

		\AXC{}
		\RightLabel{$Id$}
		\UIC{$B \Rightarrow B$}
		\RightLabel{$L\land_2$}
		\UIC{$A \land B \Rightarrow B$}
		\RightLabel{$N$} \doubleLine	
		\UIC{$\nabla^n (A \land B) \Rightarrow \nabla^n B$}
		
		\RightLabel{$R\land$}
		\BIC{$\nabla^n (A \land B) \Rightarrow \nabla^n A \land \nabla^n B$}
	\end{prooftree}
\end{proof}

\begin{lem}\label{lem:l-nabla-dist-or} $\mathbf{LDL} \vdash \nabla (A \lor B) \Rightarrow \nabla A \lor \nabla B$.
\end{lem}
\begin{proof}\quad
	\begin{prooftree}
		\AXC{}
		\RightLabel{$Id$}
		\UIC{$\nabla A \Rightarrow \nabla A$}
		\RightLabel{$R\lor_1$}
		\UIC{$\nabla A \Rightarrow \nabla A \lor \nabla B$}
		\RightLabel{$R\Box$}
		\UIC{$A \Rightarrow \Box (\nabla A \lor \nabla B)$}

		\AXC{}
		\RightLabel{$Id$}
		\UIC{$\nabla B \Rightarrow \nabla B$}
		\RightLabel{$R\lor_2$}
		\UIC{$\nabla B \Rightarrow \nabla A \lor \nabla B$}
		\RightLabel{$R\Box$}
		\UIC{$B \Rightarrow \Box (\nabla A \lor \nabla B)$}

		\RightLabel{$L\lor$}
		\BIC{$A \lor B \Rightarrow \Box (\nabla A \lor \nabla B)$}
		\RightLabel{$N$}
		\UIC{$\nabla (A \lor B) \Rightarrow \nabla \Box (\nabla A \lor \nabla B)$}

		
		\AXC{} \RightLabel{$Id$}
		\UIC{$\nabla A \lor \nabla B \Rightarrow \nabla A \lor \nabla B$}
		\RightLabel{$L\Box$}
		\UIC{$\nabla \Box (\nabla A \lor \nabla B) \Rightarrow \nabla A \lor \nabla B$}



		\RightLabel{$Cut$}
		\BIC{$\nabla (A \lor B) \Rightarrow \nabla A \lor \nabla B$}
	\end{prooftree}
\end{proof}

\begin{lem}\label{lem:l-nabla-n-dist-or} For all $n > 0$, $\mathbf{LDL} \vdash \nabla^n (A \lor B) \Rightarrow \nabla^n A \lor \nabla^n B$.
\end{lem}
\begin{proof} Let $\mathcal{D}_1$ be the proof-tree of lemma \ref{lem:l-nabla-dist-or}, which proves $n = 1$ case. For $n > 1$

	\begin{prooftree}
		\AXC{$\mathcal{D}_{n-1}$}
		\noLine
		\UIC{$\nabla^{n-1} (A \lor B) \Rightarrow \nabla^{n-1} A \lor \nabla^{n-1} B$}
		\RightLabel{$N$}
		\UIC{$\nabla^n (A \lor B) \Rightarrow \nabla (\nabla^{n-1} A \lor \nabla^{n-1} B)$}

		\AXC{$\mathcal{D}_1$}
		\noLine
		\UIC{$\nabla (\nabla^{n-1} A \lor \nabla^{n-1} B) \Rightarrow \nabla^n A \lor \nabla^n B$}
		
		\RightLabel{$Cut$} \LeftLabel{$\mathcal{D}_n:$}
		\BIC{$\nabla^n (A \lor B) \Rightarrow \nabla^n A \lor \nabla^n B$}
	\end{prooftree}
\end{proof}

\begin{lem}\label{lem:l-nabla-bot} $\mathbf{LDL} \vdash \nabla \bot \Rightarrow \bot$.
\end{lem}
\begin{proof}\quad
	\begin{prooftree}
		\AXC{}
		\RightLabel{$Ex$}
		\UIC{$\bot \Rightarrow$}
		\RightLabel{$Rw$}
		\UIC{$\bot \Rightarrow \Box \bot$}
		\RightLabel{$N$}
		\UIC{$\nabla \bot \Rightarrow \nabla \Box \bot$}

		\AXC{} \RightLabel{$Id$}
		\UIC{$\bot \Rightarrow \bot$}
		\RightLabel{$L\Box$}
		\UIC{$\nabla \Box \bot \Rightarrow \bot$}
		
		\RightLabel{$Cut$}
		\BIC{$\nabla \bot \Rightarrow \bot$}
	\end{prooftree}
\end{proof}

\begin{lem}\label{lem:l-nabla-n-bot} For $n > 0$, $\mathbf{LDL} \vdash \nabla^n \bot \Rightarrow \bot$.
\end{lem}
\begin{proof} We will prove a stronger version: For $n \geq m > 0$, $\mathbf{LDL} \vdash \nabla^n \bot \Rightarrow \nabla^{n-m} \bot$. Let $\mathcal{D}_1$ be the proof-tree of lemma \ref{lem:l-nabla-bot} which handles $n = m = 1$. Using induction om $m$, and denoting by IH the proof-tree for $\nabla^n \bot \Rightarrow \nabla^{n-(m-1)} \bot$ from the induction hypothesis, we have for $n > 1$
	\begin{prooftree}
		\AXC{IH}
		\noLine
		\UIC{$\nabla^n \bot \Rightarrow \nabla^{n-(m-1)} \bot$}

		\AXC{$\mathcal{D}_1$}
		\noLine
		\UIC{$\nabla \bot \Rightarrow \bot$}
		\doubleLine \RightLabel{$N^{(n-m)}$}
		\UIC{$\nabla^{n-(m-1)} \bot \Rightarrow \nabla^{n-m} \bot$}

		\RightLabel{$Cut$}
		\BIC{$\nabla^n \bot \Rightarrow \nabla^{n-m} \bot$}
	\end{prooftree}
\end{proof}

\begin{cor}
	All proof-trees of the lemmas \ref{lem:l-nabla-dist-and}, \ref{lem:l-nabla-dist-or}, \ref{lem:l-nabla-n-dist-or}, \ref{lem:l-nabla-bot} and \ref{lem:l-nabla-n-bot} can be easily constructed in $\mathbf{LDL}_{\rightsquigarrow}$. Hence the these lemmas also hold for $\mathbf{LDL}_{\rightsquigarrow}$.
\end{cor}

\begin{lem}\label{lem:l-nabla-dist-imp} For any $n > 0$, $\mathbf{LDL} \vdash \nabla^n (A \rightarrow B) \Rightarrow \nabla^n A \rightarrow \nabla^n B$.
\end{lem}
\begin{proof}\quad
	\begin{prooftree}
		\AXC{}
		\RightLabel{$Id$}
		\UIC{$A \Rightarrow A$}
	
		\AXC{}
		\RightLabel{$Id$}
		\UIC{$B \Rightarrow B$}
		\RightLabel{$Lw$}
		\UIC{$A , B \Rightarrow B$}
	
		\RightLabel{$L\rightarrow$}
		\BIC{$A \rightarrow B , A \Rightarrow B$}
		\RightLabel{$N^{(n)}$} \doubleLine
		\UIC{$\nabla^n (A \rightarrow B) , \nabla^n A \Rightarrow \nabla^n B$}
		\RightLabel{$R\rightarrow$}
		\UIC{$\nabla^n (A \rightarrow B) \Rightarrow \nabla^n A \rightarrow \nabla^n B$}
	\end{prooftree}
\end{proof}

\begin{lem}\label{lem:l-nabla-box-comm} For all $n > 0$, $\mathbf{LDL} \vdash \nabla^{n+1} \Box A \Rightarrow \nabla \Box \nabla^n A$.
\end{lem}
\begin{proof}\quad
	\begin{prooftree}
		\AXC{} \RightLabel{$Id$}
		\UIC{$A \Rightarrow A$}
		\RightLabel{$L\Box$}
		\UIC{$\nabla \Box A \Rightarrow A$}
		\RightLabel{$N^{(n)}$} \doubleLine
		\UIC{$\nabla^{n+1} \Box A \Rightarrow \nabla^n A$}
		\RightLabel{$R\Box$}
		\UIC{$\nabla^n \Box A \Rightarrow \Box \nabla^n A$}
		\RightLabel{$N$}
		\UIC{$\nabla^{n+1} \Box A \Rightarrow \nabla \Box \nabla^n A$}
	\end{prooftree}
\end{proof}

\begin{lem}\label{lem:sl-nabla-dist-si} For any $n > 0$, $\mathbf{LDL}_{\rightsquigarrow} \vdash \nabla^n (A \rightsquigarrow B) \Rightarrow \nabla^n A \rightsquigarrow \nabla^n B$.
\end{lem}
\begin{proof}\quad
	\begin{prooftree}
		\AXC{}
		\RightLabel{$Id$}
		\UIC{$A \Rightarrow A$}
		
		\AXC{}
		\RightLabel{$Id$}
		\UIC{$B \Rightarrow B$}
		\RightLabel{$Lw$}
		\UIC{$A , B \Rightarrow B$}
		
		\RightLabel{$L\rightsquigarrow$}
		\BIC{$\nabla (A \rightsquigarrow B) , A \Rightarrow B$}
		\RightLabel{$N^{(n)}$} \doubleLine
		\UIC{$\nabla^{n+1} (A \rightsquigarrow B) , \nabla^n A \Rightarrow \nabla^n B$}
		\RightLabel{$R\rightsquigarrow$}
		\UIC{$\nabla^n (A \rightsquigarrow B) \Rightarrow \nabla^n A \rightsquigarrow \nabla^n B$}
	\end{prooftree}
\end{proof}

\begin{cor}
	Since $\mathbf{LDL}^*$ ($\mathbf{LDL}^*_{\rightsquigarrow}$) is just a generalization of $\mathbf{LDL}$ ($\mathbf{LDL}_{\rightsquigarrow}$), then all the above lemmas also hold for $\mathbf{LDL}^*$ ($\mathbf{LDL}^*_{\rightsquigarrow}$).
\end{cor}

In the rest of this section, by the \emph{length of a proof-tree} $\mathcal{D}$, denoted by $h(\mathcal{D})$, we mean the number of rule instances in its longest branch.

\begin{thm}\label{thm:ldl-eq-ldls}
	For any sequent $\Gamma \Rightarrow \Delta$ in the language $\mathcal{L}$, $\mathbf{LDL} \vdash \Gamma \Rightarrow \Delta$ iff $\mathbf{LDL}^* \vdash \Gamma \Rightarrow \Delta$.
\end{thm}
\begin{proof}
	One direction easily follows from the fact that all rules of $\mathbf{LDL}$ are just instances of $\mathbf{LDL}^*$'s rules.
	For the other direction, we will use case analysis for the last rule of the proof-tree of $\Gamma \Rightarrow \Delta$ in $\mathbf{LDL}^*$, which we call $\mathcal{D}$, and construct a proof-tree for it in $\mathbf{LDL}$ for each case.
	
	First notice that $Id$ and $Ta$ are present in $\mathbf{LDL}$ and lemma \ref{lem:l-nabla-n-bot} handles the $Ex$ case.
	For other rules, use induction on the length of $\mathcal{D}$.
	So for the sequents proved by sub-tree(s) of $\mathcal{D}$, the induction hypothesis provides proof of the same sequent(s) in $\mathbf{LDL}$.
	For common rules, just apply the same rule (in $\mathbf{LDL}$) on the proof-tree(s) from the induction hypothesis to reach the desired sequent.
	In cases of $\mathbf{LDL}^*$'s stronger rules, i.e. $L\land_1$, $L\land_2$, $L\lor$, $L\rightarrow$ and $L\Box$, do the same, and also $cut$ sequents from lemmas \ref{lem:l-nabla-dist-and}, \ref{lem:l-nabla-dist-or}, \ref{lem:l-nabla-dist-imp} or \ref{lem:l-nabla-box-comm} into the resulting sequent.
	The case for $N$ divides to two further cases. One case is when $\Delta = A$ for some formula $A$, which is again handled by applying $N$ on the sequent from the induction hypothesis.
	The other case is when $\Delta = \{\}$, so we have $\Gamma \Rightarrow$ from induction hypothesis, in which we first introduce $\bot$ on the right using $Rw$ and apply $N$.
	Then we can $cut$ it into the sequent from lemma \ref{lem:l-nabla-bot}, and then into $Ex$, just to derive $\nabla \Gamma \Rightarrow$ as was desired.
\end{proof}

\begin{thm}\label{thm:sldl-eq-sldls}
	For any sequent $\Gamma \Rightarrow \Delta$ in the language $\mathcal{L}_{\rightsquigarrow}$, $\mathbf{LDL}_{\rightsquigarrow} \vdash \Gamma \Rightarrow \Delta$ iff $\mathbf{LDL}^*_{\rightsquigarrow} \vdash \Gamma \Rightarrow \Delta$.
\end{thm}
\begin{proof}
	The proof is similar to the proof of previous theorem, except that we don't have a case for $L\Box$ and there is a case for $L\rightsquigarrow$ instead of $L\rightarrow$, which is handled similarly, with the help of lemma \ref{lem:sl-nabla-dist-si}.
\end{proof}

\subsection{Cut-elimination theorems}
Although the admissibility of cut in $\mathbf{LDL}^*$ and $\mathbf{LDL}^*_{\rightsquigarrow}$ does not imply it's admissibility in $\mathbf{LDL}$ or $\mathbf{LDL}_{\rightsquigarrow}$, but as we will see, their equivalence ---by theorems \ref{thm:ldl-eq-ldls} and \ref{thm:sldl-eq-sldls} respectively--- enables us to prove statements about the cut-free system, which are otherwise not provable in the presence of the cut rule, and translate the result back into statements about the original system.

For technical reasons, we will eliminate a stronger form of the cut rule, which nevertheless satisfies our goal here. From here on, by $\{\nabla^{n_i} A\}$ ($\{\nabla^{n_i} \Gamma\}$) we mean the multi-set $\{ \nabla^{n_0} A, \dots, \nabla^{n_k} A \}$ ($\bigcup_{A \in \Gamma} \{\nabla^{n_i} A\}$) for some sequence of natural numbers $\{n_i\}$ of length $k+1$.

\begin{dfn}[Multi-cut rule] We denote by $\mathbf{LDL}^{*M}$ ($\mathbf{LDL}^{*M}_{\rightsquigarrow}$) the same system defined by $\mathbf{LDL}^*$ ($\mathbf{LDL}^*_{\rightsquigarrow}$), with the cut rule replaced by the following generalization:
\begin{prooftree}
	\AXC{$\Gamma \Rightarrow \nabla^m A$}
	\AXC{$\Sigma , \{\nabla^{n_i} A\} \Rightarrow \Delta$}
	\RightLabel{$\nabla Cut$}
	\BIC{$\{\nabla^{n_i} \Gamma\} , \nabla^m \Sigma \Rightarrow \nabla^m \Delta$}
\end{prooftree}
where $\nabla^n$ means $\nabla$ applied $n$ times and $\{\nabla^{n_i} A\}$ for some sequence of natural numbers $n_i$ of length $l$ means $\{\nabla^{n_0} A,\dotsb, \nabla^{n_l} A\}$.
We call $A$ the \emph{cut-formula} and for convenience, will refer to members of $\{\nabla^m A\} \cup \{\nabla^{n_i} A\}$ as \emph{cut-burden}. We will also denote by the tuple $(A, m, \{n_i\})$, the \emph{cut data} of such instance.
\end{dfn}

\begin{cor}\label{cor:mc-riddance} Any sequent provable in $\mathbf{LDL}^*$ ($\mathbf{LDL}^*_{\rightsquigarrow}$) is also provable in $\mathbf{LDL}^{*M}$ ($\mathbf{LDL}^{*M}_{\rightsquigarrow}$). Indeed we can just replace any instance of $cut$ with similar instance of $MC$, with $m = 0$ and $n_i = (0)$.
\end{cor}

Next, we should make precise what we mean by the \emph{rank} of formulas and proof-trees.

\begin{dfn}[Rank]
	Rank of a formula $A$ is defined as
	\[ \rho(A) = \begin{cases}
	1 & \quad ; A \in P \cup \{ \bot, \top \} \\
	\rho(B) & \quad ; A = \nabla B \\
	\rho(B) + 1 & \quad ; A = \Box B \\
	max(\rho(B), \rho(C)) + 1 & \quad ; A = B \circ C, \circ \in \{ \land , \lor, \rightarrow \}
	\end{cases} \]
	Notice that $\nabla$ does not increase rank.
	
	We also define rank for rule instances and proof-trees. Rank of a rule instance is the rank of its cut-formula if it is an instance of the $\nabla Cut$ rule, and $0$ if it's not.
	For a proof tree $\mathcal{D}$, $\rho(\mathcal{D})$ is the maximum rank of its rule instances.
\end{dfn}

The following lemma will help us in the proof of the next theorem.

\begin{lem}\label{lem:ldls-top-redundant} If $\mathbf{LDL}^{*M}$ ($\mathbf{LDL}^{*M}_{\rightsquigarrow}$) proves $\Gamma , \{\nabla^{n_i} \top\} \Rightarrow \Delta$, then it also proves $\Gamma \Rightarrow \Delta$ with a proof-tree of at most the same rank.
\end{lem}
\begin{proof}
Suppose $\mathcal{D}$ is a proof-tree for $\Gamma , \{\nabla^{n_i} \top\} \Rightarrow \Delta$ in $\mathbf{LDL}^{*M}$. By induction on $h(\mathcal{D})$, induction hypothesis states that for an arbitrary proof tree $\mathcal{D}'$ with conclusion $\Gamma' , \{\nabla^{n_i'} \top\} \Rightarrow \Delta'$ such that $h(\mathcal{D}') < h(\mathcal{D})$, there is a proof $\mathcal{D}''$ of $\Gamma' \Rightarrow \Delta'$ such that $\rho(\mathcal{D}'') \leq \rho(\mathcal{D}')$. Notice that induction hypothesis is applicable to any proof tree of lower length, with no restrictions on $\Gamma'$, $\Delta'$, $n'$ or $r'$.

Consider different cases for the last rule of $\mathcal{D}$, with possible sub-trees $\mathcal{D}_0$ and $\mathcal{D}_1$. $Ta$ and $Ex$ cases are trivially ruled out. In $Id$ case, which implies $\{\nabla^{n_i} \top\} = \nabla^n \top$ for some $n$, we have $\Rightarrow \nabla^n \top$ by $n$ times applications of $N$ on $Ta$. In $Lw$ case, where $\{\nabla^{n_i} \top\} = \nabla \top$ and it is principal, $\mathcal{D}_0$ itself proves the desired sequent. If $\{\nabla^{n_i} \top\}$ has more members, then the induction hypothesis gives the desired sequent. $Lc$ on some $\nabla^{n_j} \top$ is similar. In all other cases, just apply induction hypothesis on $\mathcal{D}_0$ (and possibly $\mathcal{D}_1$), then the same last rule. Notice that in the case for $N$ we apply the induction hypothesis with $n_i' = n_i - 1$. Also notice that $\nabla Cut$ is not used except in $\nabla Cut$ case, where it is applied with the same cut-formula, so the resulting proof tree is not of a higher rank than $\mathcal{D}$.

The proof for $\mathbf{LDL}^{*M}_{\rightsquigarrow}$ is similar, except that there are no cases for $\Box$, and there are cases for $\rightsquigarrow$ instead of $\rightarrow$. The case for $L\rightsquigarrow$ is handled similar to $L\rightarrow$, but in $R\rightsquigarrow$ case, we must apply the induction hypothesis with $n_i' = n_i + 1$.
\end{proof}

The following theorem shows that we can imitate any instance of the cut rule in a proof-tree of lower rank.

\begin{thm}\label{thm:ldls-cut-reduction}[Cut Reduction]
Let $\mathbf{S}$ be the any of systems $\mathbf{LDL}^{*}$, $\mathbf{LDL}^{*}_{\rightsquigarrow}$, or one of them supplemented with any one of the rules $L$, $R'$, $Fa$($Fa_\rightsquigarrow$) or $Fu'$. If $\mathbf{S} + \nabla Cut$ proves $\Gamma \Rightarrow \nabla^m A$ and $\Sigma , \{\nabla^{n_i} A\} \Rightarrow \Delta$ with proof trees of ranks less than $\rho(A)$, then it also proves $\{\nabla^{n_i} \Gamma\} , \nabla^m\Sigma \Rightarrow \nabla^m\Delta$ also with a proof tree of a rank less than $\rho(A)$.
\end{thm}
\begin{proof}
	We have two proof-trees
  \[
    {\mathcal{D}_0
    \atop
    \Gamma \Rightarrow \nabla^m A}
    \hspace{3em}
    {\mathcal{D}_1
    \atop
    \Sigma , \{\nabla^{n_i} A\} \Rightarrow \Delta}
  \]
  both of a lower rank than that of $A$, and we want to construct a proof-tree
  \[\mathcal{D} \atop \{\nabla^{n_i} \Gamma\} , \nabla^m \Sigma \Rightarrow \nabla^m \Delta \]
  without increasing the cut rank.

	The construction takes place in different cases for the last rule that occurs in $\mathcal{D}_0$ and $\mathcal{D}_1$. Notice that proof of the theorem is essentially the same for all systems, modulo the cases that are specific to each system. Thus, the cases which are common between all systems are not repeated for the sake of brevity.

	Also notice that in some cases our construction would depend only on the last rule of one of the sub-trees, i.e. it would work no matter what the last rule in $\mathcal{D}_1$ is. so it will cover all the cases for the other sub-tree. In other cases, which are the cases that the cut-formula is altered on both sides, the last rule in one sub-tree determines a specific form for the cut-formula, which in turn determines the last rule of the other sub-tree.


	First, construct the desired proof-tree in the cases that $\mathcal{D}_0$ is an axiom, independent of $\mathcal{D}_1$. The case for $Id$ is trivial, $Ex$ won't happen and $Ta$ is handled by lemma \ref{lem:ldls-top-redundant}.

  In rest of the cases, we will use induction on the length of both $\mathcal{D}_0$ and $\mathcal{D}_1$ as follows; For any two proof-trees $\mathcal{D}_0'$ and $\mathcal{D}_1'$ such that $h(\mathcal{D}_0') + h(\mathcal{D}_1') < h(\mathcal{D}_0) + h(\mathcal{D}_1)$, where $\mathcal{D}_0'$ proves $\Gamma' \Rightarrow \nabla^{m'} A'$ and $\mathcal{D}_1'$ proves $\Sigma', \{\nabla^{n'_i} A'\} \Rightarrow \Delta'$ for arbitrary $\Gamma'$, $\Sigma'$, $\Delta'$, $A'$, $m'$ and $n_i'$, for which we have $\rho(\mathcal{D}_0'),\mathcal{D}_1' < \rho(A')$, the induction hypothesis give us a proof-tree $\text{IH}(\mathcal{D}_0', \mathcal{D}_1')$ that proves $\{\nabla^{n_i'}\Gamma'\}, \nabla^{m'} \Sigma' \Rightarrow \nabla^{m'} \Delta'$, and we also have $\rho(\text{IH}(\mathcal{D}_0', \mathcal{D}_1')) < \rho(A')$.


	Assume $\mathcal{D}_0$ ends with an instance of any of the rules $Lw$, $Lc$, $L\land_1$, $L\land_2$, $L\lor$, $L\rightarrow$, $L\rightsquigarrow$, $L\Box$, $\nabla Cut$, $N$, $Fu'$, $L$ or $R'$, again independent of $\mathcal{D}_1$. In all these cases, it suffices to use induction on the assumption(s) of this rule to remove the cut-burden from both sub-trees. Then, we can apply the same rule to get the desired sequent. Here we will only mention the cases for $L\wedge_1$, $L\vee$, $L\rightsquigarrow$, $\nabla Cut$, $N$ and $Fu'$, the last three of which may be of special concern, since they also alter the cut-burden.

	$L\wedge_1$: If $\mathcal{D}_0$ ends with $L\wedge_1$, that is
	\begin{prooftree}
		\noLine
		\AXC{$\mathcal{D}_0'$}
		\UIC{$\Gamma, \nabla^r B \Rightarrow \nabla^m A$}
		
		\RightLabel{$L\wedge_1$}
		\UIC{$\Gamma, \nabla^r (B \wedge C) \Rightarrow \nabla^m A$}
 \end{prooftree}
 then by applying $L\wedge_1$ on what we get from induction
 \begin{prooftree}
	\noLine
	\AXC{$\mathcal{D}_0'$}
	\UIC{$\Gamma, \nabla^r B \Rightarrow \nabla^m A$}
	
	\noLine
	\AXC{$\mathcal{D}_1$}
	\UIC{$\Sigma , \{\nabla^{n_i} A\} \Rightarrow \Delta$}
	
	\RightLabel{IH}
	\BIC{$\{\nabla^{n_i} \Gamma, \nabla^{n_i+r} B\}, \nabla^m \Sigma \Rightarrow \nabla^m \Delta$}

	\RightLabel{$L\wedge_1$} \doubleLine
	\UIC{$\{\nabla^{n_i} \Gamma, \nabla^{n_i+r} (B \wedge C)\}, \nabla^m \Sigma \Rightarrow \nabla^m \Delta$}
 \end{prooftree}

 \noindent $L\vee$: If $\mathcal{D}_0$ ends with $L\vee$
	 \begin{prooftree}
		 \noLine
		 \AXC{$\mathcal{D}_0'$}
		 \UIC{$\Gamma, \nabla^r B \Rightarrow \nabla^m A$}
		 
		 \noLine
		 \AXC{$\mathcal{D}_0''$}
		 \UIC{$\Gamma, \nabla^r C \Rightarrow \nabla^m A$}
		 
		 \RightLabel{$L\vee$}
		 \BIC{$\Gamma, \nabla^r (B \vee C) \Rightarrow \nabla^m A$}
	\end{prooftree}
	Applying $L\vee$ on the sequents that we get from induction
	\begin{prooftree}
    \noLine
		\AXC{$\mathcal{D}_0'$}
		\UIC{$\Gamma, \nabla^r B \Rightarrow \nabla^m A$}
		
		\noLine
		\AXC{$\mathcal{D}_1$}
		\UIC{$\Sigma , \{\nabla^{n_i} A\} \Rightarrow \Delta$}
		
		\RightLabel{IH}
		\BIC{$\{\nabla^{n_i} \Gamma, \nabla^{n_i+r} B\}, \nabla^m \Sigma \Rightarrow \nabla^m \Delta$}
		

    \noLine
		\AXC{$\mathcal{D}_0''$}
		\UIC{$\Gamma, \nabla^r C \Rightarrow \nabla^m A$}
		
		\noLine
		\AXC{$\mathcal{D}_1$}
		\UIC{$\Sigma , \{\nabla^{n_i} A\} \Rightarrow \Delta$}
		
		\RightLabel{IH}
    \BIC{$\{\nabla^{n_i} \Gamma, \nabla^{n_i+r} C\}, \nabla^m \Sigma \Rightarrow \nabla^m \Delta$}

		\RightLabel{$L\vee$}
		\BIC{$\{\nabla^{n_i} \Gamma, \nabla^{n_i+r} (B \vee C)\}, \nabla^m \Sigma \Rightarrow \nabla^m \Delta$}
	 \end{prooftree}

 
\noindent $L\rightsquigarrow$: Suppose $\mathcal{D}_0$ ends with a $L\rightsquigarrow$ as shown below.
 \begin{prooftree}
  \noLine
  \AXC{$\mathcal{D}_0'$}
  \UIC{$\Gamma \Rightarrow \nabla^r B$}
  \noLine
  \AXC{$\mathcal{D}_0''$}
  \UIC{$\Gamma , \nabla^r C \Rightarrow \nabla^m A$}
  \RightLabel{$L\rightsquigarrow$}
  \BIC{$\Gamma , \nabla^{r+1} (B \rightsquigarrow C) \Rightarrow \nabla^m A$}
 \end{prooftree}
 From induction hypothesis we have
 \begin{prooftree}
  \noLine
  \AXC{$\mathcal{D}_0''$}
  \UIC{$\Gamma , \nabla^r C \Rightarrow \nabla^m A$}
  \noLine
  \AXC{$\mathcal{D}_1$}
  \UIC{$\Sigma , \{\nabla^{n_i} A\} \Rightarrow \Delta$}
  \RightLabel{IH} \LeftLabel{$\mathcal{D}':~~~~$}
  \BIC{$\{\nabla^{n_i} \Gamma , \nabla^{n_i+r} C\} , \nabla^m \Sigma \Rightarrow \nabla^m \Delta$}
 \end{prooftree}
 In order to apply $L\rightsquigarrow$, we must prepare the context in $\mathcal{D}_0'$, for each of $\nabla^{n_i+r}C$'s. Beginning with $n_0$, first we need to apply $N$ on $\mathcal{D}_0'$ $n_0$ times to get $\nabla^{n_0}\Gamma$ on the left and $\nabla^{n_0+r} B$ on the right side. Then we can just add the rest of the context by $Lw$.
 \begin{prooftree}
  \noLine
  \AXC{$\mathcal{D}_0'$}
  \UIC{$\Gamma \Rightarrow \nabla^r B$}
  \doubleLine \RightLabel{$N$}
  \UIC{$\nabla^{n_0} \Gamma \Rightarrow \nabla^{n_0+r} B$}
  \doubleLine \RightLabel{$Lw$} \LeftLabel{$\mathcal{D}'_{n_0}:~~~~$}
  \UIC{$\nabla^{n_0}\Gamma, \{\nabla^{n_i} \Gamma, \nabla^{n_i+r}C\}_{i>0} , \nabla^m \Sigma \Rightarrow \nabla^{n_0+r} B$}
 \end{prooftree}
 By $L\rightsquigarrow$ on $\mathcal{D}'$ and $\mathcal{D}'_{n_0}$, we have
 \[\nabla^{n_0}\Gamma, \{\nabla^{n_i} \Gamma, \nabla^{n_i+r}C\}_{i>0}, \nabla^{n_0+r+1} (B \rightsquigarrow C) , \nabla^m \Sigma \Rightarrow \nabla^m \Delta\]
 We can repeat for this all of $n_i$'s to get
 \[\{\nabla^{n_i} \Gamma, \nabla^{n_i+r+1}(B \rightsquigarrow C)\}, \nabla^m \Sigma \Rightarrow \nabla^m \Delta\]
 which is the desired sequent.


 $\nabla Cut$: Assume $\mathcal{D}_0$ ends with a $\nabla Cut$ with cut-data $(A', m', \{n_i'\})$. Notice that by assumption, $A'$ must have a lower rank than $A$.
 \begin{prooftree}
   \noLine
   \AXC{$\mathcal{D}_0'$}
   \UIC{$\Gamma \Rightarrow \nabla^{m'} A'$}
   
   \noLine
   \AXC{$\mathcal{D}_0''$}
   \UIC{$\Pi , \{\nabla^{n_i'} A'\} \Rightarrow \nabla^m A$}
   
   \RightLabel{$\nabla Cut$}
   \BIC{$\{\nabla^{n_i'} \Gamma\} , \nabla^{m'} \Pi \Rightarrow \nabla^{m+m'} A$}
 \end{prooftree}
 We must construct a proof-tree for $\{\nabla^{n_i}\{\nabla^{n_i'} \Gamma\}, \nabla^{n_i+m'} \Pi\} , \nabla^{m+m'}\Sigma \Rightarrow \nabla^{m+m'}\Delta$. We can use the induction hypothesis to remove $A$ first, then cut $A'$.
 \begin{prooftree}
   \noLine
   \AXC{$\mathcal{D}_0'$}
   \UIC{$\Gamma \Rightarrow \nabla^{m'} A'$}
   
   \noLine
   \AXC{$\mathcal{D}_0''$}
   \UIC{$\Pi , \{\nabla^{n_i'} A'\} \Rightarrow \nabla^m A$}

   \noLine
   \AXC{$\mathcal{D}_1$}
   \UIC{$\Sigma , \{\nabla^{n_i} A\} \Rightarrow \Delta$}

   \RightLabel{IH}
   \BIC{$\{\nabla^{n_i} \Pi , \nabla^{n_i}\{\nabla^{n_i'} A'\}\} , \nabla^m \Sigma \Rightarrow \nabla^m \Delta$}
   

   \RightLabel{$MC$}
   \BIC{$\{\nabla^{n_i}\{\nabla^{n_i'} \Gamma\}, \nabla^{n_i+m'} \Pi\} , \nabla^{m+m'}\Sigma \Rightarrow \nabla^{m+m'}\Delta$}
 \end{prooftree}

 $Rw$: In this case, $\mathcal{D}_0'$ proves $\Gamma \Rightarrow$, so we can simply construct the desired proof-tree using $N$, $Lw$ and $Rw$.
 \begin{prooftree}
   \noLine
   \AXC{$\mathcal{D}_0'$}
   \UIC{$\Gamma \Rightarrow$}
   \doubleLine \RightLabel{$N$}
   \UIC{$\nabla^{n_0} \Gamma \Rightarrow$}
   \doubleLine \RightLabel{$Lw$}
   \UIC{$\{\nabla^{n_i} \Gamma\} , \nabla^m \Sigma \Rightarrow$}
   \RightLabel{$Rw$}
   \UIC{$\{\nabla^{n_i} \Gamma\} , \nabla^m \Sigma \Rightarrow \nabla^m \Delta$}
 \end{prooftree}

 $N$: $\mathcal{D}_0$ proves $\nabla \Gamma \Rightarrow \nabla^{m+1} A$ and the cut-formula is in the form $\nabla A$. So we want to construct $\{\nabla^{n_i+1}\Gamma\}, \nabla^m \Sigma \Rightarrow \nabla^m \Delta$. Induction hypothesis for $\mathcal{D}_0$'s immediate sub-tree and $\mathcal{D}_1$ gives us exactly what we want.

 $Fu'$: It suffices to apply $Fu'$ on the result of the induction.\\

 The rest of the cases for $\mathcal{D}_0$ can't be solved independent of $\mathcal{D}_1$, so we will consider cases for the last rule of $\mathcal{D}_1$, again, where they're handled independent of $\mathcal{D}_0$. But this time we have much less possibilities for the opposite sub-tree, since we've already solved many of them. In fact the only possible rules for the last rule of $\mathcal{D}_0$ are now $R\star (\star \in \{\land, \lor_{1/2}, \rightarrow, \Box, \rightsquigarrow\})$, $Fa$ and $Fa_\rightsquigarrow$.

 This time, suppose $\mathcal{D}_1$ is and axiom. Again, the $Id$ case is trivial, $Ta$ won't happen, and $Ex$ is also infeasible, since all possible rules for $\mathcal{D}_0$ alter the right side of the sequent, but none of them is able to introduce $\bot$ there.

 Next, for cases that the cut-burden is not altered (modulo $\nabla$) in the last rule of $\mathcal{D}_1$, the construction is similar to the previous cases: Applying the same rule on the sequent that we get from the induction hypothesis. For the sake of briefness, we will mention only cases for $L\wedge_1$, $R\vee_1$, $R\rightsquigarrow$ and $N$.

 $L\wedge$: Assume that $\mathcal{D}_1$ ends with $L\wedge_1$, but no member of the cut-burden is it's principal formula.
 \begin{prooftree}
	\AXC{$\mathcal{D}_1'$} \noLine
	\UIC{$\Sigma, \{\nabla^{n_i} A\}, \nabla^r B \Rightarrow \Delta$}
	\RightLabel{$L\wedge_1$}
	\UIC{$\Sigma, \{\nabla^{n_i} A\}, \nabla^r (B \wedge C) \Rightarrow \Delta$}
 \end{prooftree}
 From induction hypothesis we have $\{\nabla^{n_i} \Gamma\}, \nabla^m \Sigma, \nabla^{r+m} B \Rightarrow \nabla^m \Delta$. By $L\wedge_1$ we have $\{\nabla^{n_i} \Gamma\}, \nabla^m \Sigma, \nabla^{r+m} (B \wedge C) \Rightarrow \nabla^m \Delta$.

 $R\vee_1$: Suppose that $\mathcal{D}_1$ ends with $L\vee_1$ and its principal formula is not in the cut-burden.
 \begin{prooftree}
	\AXC{$\mathcal{D}_1'$} \noLine
	\UIC{$\Sigma, \{\nabla^{n_i} A\} \Rightarrow \nabla^r B$}
	\RightLabel{$L\vee_1$}
	\UIC{$\Sigma, \{\nabla^{n_i} A\} \Rightarrow \nabla^r (B \vee C)$}
 \end{prooftree}
 Again, use the induction hypothesis to get $\{\nabla^{n_i} \Gamma\}, \nabla^m\Sigma \Rightarrow \nabla^{r+m} B$, then apply $L\vee_1$ to reach the desired sequent.

$R\rightsquigarrow$: In the case where $\mathcal{D}_1$ ends with an $R\rightsquigarrow$, the cut-burden is altered in the premise. So the induction hypothesis has a different cut-data. nevertheless, it still commutes with $R\rightsquigarrow$.
\begin{prooftree}
	\AXC{$\mathcal{D}_1'$} \noLine
	\UIC{$\nabla\Sigma, \{\nabla^{n_i+1} A\}, B \Rightarrow C$}
	\RightLabel{$L\rightsquigarrow$}
	\UIC{$\Sigma, \{\nabla^{n_i} A\} \Rightarrow B \rightsquigarrow C$}
 \end{prooftree}
From induction hypothesis, we have $\{\nabla^{n_i+1} \Gamma\}, \nabla^{m+1} \Sigma, \nabla^m B \Rightarrow \nabla^m C$. We can simply apply $R\rightsquigarrow$ to get $\{\nabla^{n_i} \Gamma\}, \nabla^m \Sigma \Rightarrow \nabla^m (B \rightsquigarrow C)$.

$N$: Suppose $\mathcal{D}_1$ ends with $N$.
\begin{prooftree}
	\AXC{$\mathcal{D}_1'$} \noLine
	\UIC{$\Sigma, \{\nabla^{n_i} A\} \Rightarrow \Delta$}
	\RightLabel{$N$}
	\UIC{$\nabla \Sigma, \{\nabla^{n_i+1} A\} \Rightarrow \nabla \Delta$}
\end{prooftree}
If we assume that the cut-data is $(A, m, \{n_i+1\})$, from the induction hypothesis we have $\{\nabla^{n_i} \Gamma\}, \nabla^m \Sigma \Rightarrow \nabla^m \Delta$. By $N$ we have $\{\nabla^{n_i+1} \Gamma\}, \nabla^{m+1} \Sigma \Rightarrow \nabla^{m+1} \Delta$, which is the desired sequent.
But if $m>0$, the cut-data could also be $(\nabla A, m-1, \{n_i\})$, in which case using the induction hypothesis would suffice.

 Now for the rest of the proof, we will show how the construction takes place in the cases where the cut-formula is principal in the last rule of $\mathcal{D}_1$, which can be either of $L\star (\star \in \{\land, \lor_{1/2}, \rightarrow, \Box, \rightsquigarrow\})$.
 Any of these rules imply a specific form for the cut-formula, which can also determine the rule at the end of the other proof-tree, because the cut-formula is also principal in the last rule of $\mathcal{D}_0$ (note that the only possible rules for the last rule of $\mathcal{D}_0$ are now $R\star (\star \in \{\land, \lor_{1/2}, \rightarrow, \Box, \rightsquigarrow\})$, $Fa$ and $Fa_\rightsquigarrow$).
 Now we further destruct the proof by cases for $m$.
 
 First, notice that $m > 1$ is impossible, since the only rules that introduce $\nabla$ to the right of the sequence are $Fa$ for $\mathbf{LDL}$ based systems and $Fa_\rightsquigarrow$ for $\mathbf{LDL}_\rightsquigarrow$ based ones. So suppose $m = 1$ and $\mathcal{D}_0$ end with $Fa$ (in $\mathbf{LDL}$).
 \begin{prooftree}
	 \AXC{$\mathcal{D}_0'$}
	 \noLine
	 \UIC{$\Gamma \Rightarrow A$}
	 \RightLabel{$Fa$}
	 \UIC{$\Gamma \Rightarrow \nabla \Box A$}
 \end{prooftree}
 Now the cut-formula must be of the form $\Box A$, so the only option for $\mathcal{D}_1$ is $L\Box$.
 \begin{prooftree}
	 \AXC{$\mathcal{D}_1'$}
	 \noLine
	 \UIC{$\Sigma, \{\nabla^{n_i} \Box A\}_{i>0}, \nabla^{n_0} A \Rightarrow \Delta$}
	 \RightLabel{$L\Box$}
	 \UIC{$\Sigma, \{\nabla^{n_i} \Box A\}_{i>0}, \nabla^{n_0+1} \Box A \Rightarrow \Delta$}
 \end{prooftree}
 The desired sequent is of the form $\{\nabla^{n_i} \Gamma\}_{i>0}, \nabla^{n_0+1} \Gamma, \nabla \Sigma \Rightarrow \nabla \Delta$, which can be proved by a low rank $\nabla Cut$ (with $A$ as the cut-formula) on $\mathcal{D}_0'$ and $IH(\mathcal{D}_0, \mathcal{D}_1')$.
 \begin{prooftree}
	 \AXC{$\mathcal{D}_0'$}
	 \noLine
	 \UIC{$\Gamma \Rightarrow A$}
	 \AXC{$\mathcal{D}_0$}
	 \noLine
	 \UIC{$\Gamma \Rightarrow \nabla \Box A$}
	 \AXC{$\mathcal{D}_1'$}
	 \noLine
	 \UIC{$\Sigma, \{\nabla^{n_i} \Box A\}_{i>0}, \nabla^{n_0} A \Rightarrow \Delta$}
	 \RightLabel{IH}
	 \BIC{$\{\nabla^{n_i} \Gamma\}_{i>0}, \nabla \Sigma, \nabla^{n_0+1} A \Rightarrow \nabla \Delta$}
	 \RightLabel{$\nabla Cut$}
	 \BIC{$\{\nabla^{n_i} \Gamma\}_{i>0}, \nabla^{n_0+1} \Gamma, \nabla \Sigma \Rightarrow \nabla \Delta$}
 \end{prooftree}

 \noindent Now suppose $\mathcal{D}_0$ ends with $Fa_\rightsquigarrow$ (in $\mathbf{LDL}_\rightsquigarrow$).
 \begin{prooftree}
	 \AXC{$\mathcal{D}_0'$}
	 \noLine
	 \UIC{$\Gamma, A \Rightarrow B$}
	 \RightLabel{$Fa_\rightsquigarrow$}
	 \UIC{$\Gamma \Rightarrow \nabla (A \rightsquigarrow B)$}
 \end{prooftree}
 Since the cut-formula is of the form $A \rightsquigarrow B$, $\mathcal{D}_1$ could only end with $L\rightsquigarrow$.
 \begin{prooftree}
	 \AXC{$\mathcal{D}_1'$}
	 \noLine
	 \UIC{$\Sigma, \{\nabla^{n_i} (A \rightsquigarrow B) \}_{i>0}, \Rightarrow \nabla^{n_0} A$}
	 \AXC{$\mathcal{D}_1''$}
	 \noLine
	 \UIC{$\Sigma, \{\nabla^{n_i} (A \rightsquigarrow B) \}_{i>0}, \nabla^{n_0} B \Rightarrow \Delta$}
	 \RightLabel{$L\rightsquigarrow$}
	 \BIC{$\Sigma, \{\nabla^{n_i} (A \rightsquigarrow B)\}_{i>0}, \nabla^{n_0+1} (A \rightsquigarrow B) \Rightarrow \Delta$}
 \end{prooftree}
 Again, we want to prove $\{\nabla^{n_i} \Gamma\}_{i>0}, \nabla^{n_0+1} \Gamma, \nabla \Sigma \Rightarrow \nabla \Delta$. To do so, we first apply a low rank $\nabla Cut$ (with $B$ as the cut-formula) on $\mathcal{D}_0'$ and $IH(\mathcal{D}_0, \mathcal{D}_1'')$.
 \begin{prooftree}
	 \AXC{$\mathcal{D}_0'$}
	 \noLine
	 \UIC{$\Gamma, A \Rightarrow B$}
	 \AXC{$\mathcal{D}_0$}
	 \noLine
	 \UIC{$\Gamma \Rightarrow \nabla (A \rightsquigarrow B)$}
	 \AXC{$\mathcal{D}_1''$}
	 \noLine
	 \UIC{$\Sigma, \{\nabla^{n_i} (A \rightsquigarrow B) \}_{i>0}, \nabla^{n_0} B \Rightarrow \Delta$}
	 \BIC{$\{\nabla^{n_i} \Gamma\}_{i>0}, \nabla \Sigma, \nabla^{n_0+1} B \Rightarrow \nabla \Delta$}
	 \RightLabel{$\nabla Cut$} \LeftLabel{$\mathcal{D}':~~~~~$}
	 \BIC{$\nabla^{n_0+1} \Gamma, \nabla^{n_0+1} A, \{\nabla^{n_i} \Gamma\}_{i>0}, \nabla \Sigma \Rightarrow \nabla \Delta$}
 \end{prooftree}
 Then cut $IH(\mathcal{D}_0, \mathcal{D}_1')$ (this time with $\nabla^{n_0+1} A$ as the cut-formula) into the resulting sequent.
 \begin{prooftree}
	 \AXC{$\mathcal{D}_1'$}
	 \noLine
	 \UIC{$\Sigma, \{\nabla^{n_i} (A \rightsquigarrow B) \}_{i>0}, \Rightarrow \nabla^{n_0} A$}
	 \AXC{$\mathcal{D}_0$}
	 \noLine
	 \UIC{$\Gamma \Rightarrow \nabla (A \rightsquigarrow B)$}
	 \RightLabel{IH}
	 \BIC{$\{\nabla^{n_i} \Gamma\}_{i>0}, \nabla \Sigma, \Rightarrow \nabla^{n_0 + 1} A$}

	 \AXC{$\mathcal{D}'$}

	 \RightLabel{$\nabla Cut$}
	 \BIC{$(\{\nabla^{n_i} \Gamma\}_{i>0})^2, \nabla^{n_0+1} \Gamma, (\nabla \Sigma)^2 \Rightarrow \nabla \Delta$}
	 \doubleLine \RightLabel{$Lc$}
	 \UIC{$\{\nabla^{n_i} \Gamma\}_{i>0}, \nabla^{n_0+1} \Gamma, \nabla \Sigma \Rightarrow \nabla \Delta$}
 \end{prooftree}
 When $m = 0$, each right-rule for $\mathcal{D}_1$ determines its corresponding left-rule for $\mathcal{D}_0$.

 $R\land$ and $L\land$: Suppose $\mathcal{D}_0$ ends with $R\land$ and $\mathcal{D}_1$ with either of $L\land_c ~ (c \in \{1,2\})$.
 \begin{prooftree}
	 \noLine
	 \AXC{$\mathcal{D}_0'$}
	 \UIC{$\Gamma \Rightarrow A_1$}
	 \noLine
	 \AXC{$\mathcal{D}_0''$}
	 \UIC{$\Gamma \Rightarrow A_2$}
	 \RightLabel{$R\land$}
	 \BIC{$\Gamma \Rightarrow A_1 \land A_2$}
	 
	 \noLine
	 \AXC{$\mathcal{D}_1'$}
	 \UIC{$\Sigma , \{\nabla^{n_i} (A_1 \land A_2)\}_{i>0}, \nabla^{n_0} A_c \Rightarrow \Delta$}
	 \RightLabel{$L\land_1$}
	 \UIC{$\Sigma , \{\nabla^{n_i} (A_1 \land A_2)\} \Rightarrow \Delta$}
	 
	 \noLine
	 \BIC{}
 \end{prooftree}
 $IH(\mathcal{D}_0, \mathcal{D}_1')$ proves $\{\nabla^{n_i} \Gamma\}_{i>0} , \Sigma , \nabla^{n_0} A_c \Rightarrow \Delta$. Remove $\nabla^{n_0} A_c$ with a low rank $\nabla Cut$ on this sequent and either of $\mathcal{D}_0'$ ($c = 1$) or $\mathcal{D}_0''$ ($c = 2$) to get $\{\nabla^{n_i} \Gamma\}, \Sigma \Rightarrow \Delta$.

 $R\lor$ and $L\lor$: Suppose $\mathcal{D}_0$ ends with either of $R\lor_c ~ (c \in \{1,2\})$ and $\mathcal{D}_1$ with $L\lor$.
 \begin{prooftree}
	 \noLine
	 \AXC{$\mathcal{D}_0'$}
	 \UIC{$\Gamma \Rightarrow A_c$}
	 \RightLabel{$R\lor_c$}
	 \UIC{$\Gamma \Rightarrow A_1 \lor A_2$}
 \end{prooftree}
 \begin{prooftree}
	\noLine
	\AXC{$\mathcal{D}_1'$}
	\UIC{$\Sigma , \{\nabla^{n_i} (A_1 \lor A_2)\}_{i>0} , \nabla^{n_0} A_1 \Rightarrow \Delta$}
	\noLine
	\AXC{$\mathcal{D}_1''$}
	\UIC{$\Sigma , \{\nabla^{n_i} (A_1 \lor A_2)\}_{i>0} , \nabla^{n_0} A_2 \Rightarrow \Delta$}
	\RightLabel{$L\lor$}
	\BIC{$\Sigma ,  \{\nabla^{n_i} (A_1 \lor A_2)\} \Rightarrow \Delta$}
 \end{prooftree}
 Using induction hypothesis, first remove $\{\nabla^{n_i} (A_1 \lor A_2)\}_{i>0}$ from the sub-tree of $\mathcal{D}_1$ that has $\nabla^{n_0} A_c$ ($IH(\mathcal{D}_0, \mathcal{D}_1')$ for $c = 1$, $IH(\mathcal{D}_0, \mathcal{D}_1'')$ for $c = 2$), to get $\{\nabla^{n_i} \Gamma\}_{i>0}, \Sigma , \nabla^{n_0} A_c \Rightarrow \Delta$. Then remove $\nabla^{n_0} A_c$ by a low rank $\nabla Cut$ on this sequent and $\mathbf{D_0}'$ to get $\{\nabla^{n_i} \Gamma\}, \Sigma \Rightarrow \Delta$.

 $R\rightarrow$ and $L\rightarrow$: Suppose $\mathcal{D}_0$ and $\mathcal{D}_1$ end with $R\rightarrow$ and $L\rightarrow$ respectively.
 \begin{prooftree}
	 \noLine
	 \AXC{$\mathcal{ D}_0'$}
	 \UIC{$\Gamma, A_1 \Rightarrow A_2$}
	 \RightLabel{$R\rightarrow$}
	 \UIC{$\Gamma \Rightarrow A_1 \rightarrow A_2$}        
	 \end{prooftree}
	 \begin{prooftree}
	 \noLine
	 \AXC{$\mathcal{D}_1'$}
	 \UIC{$\Sigma, \{\nabla^{n_i} (A_1 \rightarrow A_2)\}_{i>0} \Rightarrow \nabla^{n_0} A_1$}
	 \noLine
	 \AXC{$\mathcal{D}_1''$}
	 \UIC{$\Sigma, \{\nabla^{n_i} (A_1 \rightarrow A_2)\}_{i>0}, \nabla^{n_0} A_2 \Rightarrow \Delta$}
	 \RightLabel{$L\rightarrow$}
	 \BIC{$\Sigma,  \{\nabla^{n_i} (A_1 \rightarrow A_2)\} \Rightarrow \Delta$}
 \end{prooftree}
 
 $IH(\mathcal{D}_0, \mathcal{D}_1'')$ proves $\{\nabla^{n_i} \Gamma\}_{i>0}, \Sigma, \nabla^{n_0} A_2 \Rightarrow \Delta$. Applying a low rank $\nabla Cut$ on $\mathcal{D}_0'$ and this sequent removes $\nabla^{n_0} A_2$ and introduces $\nabla^{n_0} \Gamma$ and $\nabla^{n_0} A_1$ to the left. On the other hand $IH(\mathcal{D}_0, \mathcal{D}_1')$ proves $\{\nabla^{n_i} \Gamma\}_{i>0}, \Sigma, \Rightarrow \nabla^{n_0} A_1$, which we can use to also remove $\nabla^{n_0} A_1$ with another low rank cut, and then remove the extra $\nabla^{n_0} \Gamma$ and $\Sigma$ with $Lc$.

 $R\rightsquigarrow$ and $L\rightsquigarrow$: Is just like the $\rightarrow$ case. Notice that the extra $\nabla$ on the left side of the subtree of $\mathcal{D}_0$ will provide the extra $\nabla$ on the principal formula in $\mathcal{D}_1$.

 There are also two cases where the sub-trees end with $Fa$ and $L\Box$, or with $Fa_\rightsquigarrow$ and $L\rightsquigarrow$ for $\mathbf{LDL}_\rightsquigarrow$, with $m = 0$. These cases are also similar to the $m = 1$ case, except that here the cut-formula is $\nabla\Box A$.
 \vspace{5mm}

 This concludes the proof the theorem in all cases. Notice that we have a construction for any two possible pair of rules, in both systems and all their variations.

\end{proof}

\begin{thm}\label{thm:ldls-cut-elim}[Cut Elimination]
	Let \textbf{S} be the any of systems $\mathbf{LDL}^{*}$, $\mathbf{LDL}^{*}_{\rightsquigarrow}$, or one of them supplemented with any one of the rules $L$, $R'$, $Fa$($Fa_\rightsquigarrow$) or $Fu'$. For any $\Gamma$ and $\Delta$, If $\Gamma \Rightarrow \Delta$ is provable by $\mathbf{S} + \nabla Cut$, then it is so by $\mathbf{S}$.
\end{thm}
\begin{proof}
		First, we will show that for any non-zero-rank proof of $\Gamma \Rightarrow \Delta$ like $\mathcal{D}$ in $\mathbf{S} + \nabla Cut$, there is another proof of the same sequent with a lower rank. Suppose $\mathcal{D}$ has sub-tree(s) called $\mathcal{D}_0$ (and possibly $\mathcal{D}_1$). Using induction on $h(\mathcal{D})$, the induction hypothesis for $\mathcal{D}_i ~(i \in \{1,2\})$ gives us a proof-tree with the same conclusion, which we call $IH(\mathcal{D}_i)$, but with a lower rank, i.e. $\rho(IH(\mathcal{D}_i)) < \rho(\mathcal{D}_i)$. We now consider two cases for the last rule of $\mathcal{D}$

	\begin{enumerate}[label=\Roman*]
		\item If the last rule of $\mathcal{D}$ is of a lower rank than $\rho(\mathcal{D})$, i.e. the $\nabla Cut$ instance with the maximum rank is not the last rule in $\mathcal{D}$, then we can apply the same last rule on $IH(\mathcal{D}_i)$'s and get a proof of $\Gamma \Rightarrow \Delta$ with a lower rank.
		
		\item If the last rule of $\mathcal{D}$ is an instance of $\nabla Cut$ rule with a cut-formula of rank $\rho(\mathcal{D})$, then we can apply theorem \ref{thm:ldls-cut-reduction} to $IH(\mathcal{D}_0)$ and $IH(\mathcal{D}_1)$ to get the same $\nabla Cut$ with a lower rank.
	\end{enumerate}
	So for any proof of $\Gamma \Rightarrow \Delta$ in $\mathbf{S} + \nabla Cut$, we also have a proof with rank $0$, which is cut-free.
\end{proof}

\textbf{Problem.} Do we have cut elimination theorem for the sequent-style systems we developed for $\mathbf{LDL}_{\rightsquigarrow}$ but this time plus the rule $H_{\rightsquigarrow}$? What about the system of the previous problem for $\mathbf{LDL}$ plus the rule $H$?
\subsection{Admissible Rules}
\textbf{Problem.} What are the Harrop formulas here? Prove the disjunction property for the theories axiomatized by Harrop formulas, using the cut-free proofs over the logics $\mathbf{LDL}$ and $\mathbf{LDL}_{\rightsquigarrow}$. Prove the same thing via Kleene-type argument. Do we have similar thing for the logics with added rules $H$ and $H_{\rightsquigarrow}$, respectively?
\subsection{Interpolation}
\textbf{Problem.} As we discussed, the system $\mathbf{LDL}$ and possibly $\mathbf{LDL}(H)$ must enjoy Craig interpolation property. What are the proofs?\\
\\
\textbf{Problem.} As we discussed, the system $\mathbf{LDL}_{\rightsquigarrow}$ and possibly $\mathbf{LDL}_{\rightsquigarrow}(H_{\rightsquigarrow})$ must enjoy deductive interpolation property. What are the proofs?

\begin{thebibliography}{99}
\addcontentsline{toc}{section}{References}

\bibitem{Amir}
A. Akbar Tabatabai. ``Implication via Spacetime." arXiv preprint arXiv:2001.00997 (2019).
\bibitem{Artemov}
S. Artemov, J. Davoren, and A. Nerode. Modal logics and topological semantics for hybrid systems. Technical Report MSI 97-05, 1997.
\bibitem{Ewald}
W. Ewald. Intuitionistic tense and modal logic. The Journal of Symbolic Logic, 51(1):166179, 1986.
\bibitem{Duque}
D. Fernndez-Duque. The intuitionistic temporal logic of dynamical systems. Log. Methods Comput. Sci. 14(3) (2018)
\bibitem{Mints}
P. Kremer and G. Mints. Dynamic topological logic. Annals of Pure and Applied Logic, 131:133158, 2005.

\end{thebibliography}



\end{document}
